Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
reformulate section II

As stated in the introduction, the field of ecoacoustics is relatively young, but significant works are worth mentioning.
One avenue of research, originated in bioacoustics, intends to retrieve the species that produced a given sonic event of relatively short duration, in order to link animal vocalization with behavior\cite{au2008principles, stowell2014large}.
A more recent paradigm processes the audio stream at hand in a holistic way, as it describes the auditory environment over larger temporal scales, without assuming that one single species is present throughout the recording. Automated systems belonging to this paradigm aim at inferring global properties of bioacoustic scenes, including biodiversity indices, migration patterns, as well as regions of particular interest before human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.

The same dichotomy applies for the field of audio scene analysis, where the interest can be whether 1) to isolate and identify precise events, \textit{i.e.} acoustic event detection (AED) or 2) to predict global attributes assigned to large time spans of audio, \textit{i.e.} ASC. For the latter, most state-of-the-art systems roughly follow the bag of frame approach (BOF) initiated in \cite{aucouturier2007bag} where the audio is modelled as high level statistics computed from a set of local features. Even though this approach as the advantage of high genericity and follows some evidence found by psycho perception research \cite{mcdermott2013summary}, for the specific implementation with gaussian mixture models (GMMs) of Mel-frequency cepstral coefficients (MFCCs) it is demonstrated to be perform equivalently compared to a mere point averaging of the features  \cite{lagrange:hal-01082501}.

Intuitively, this result indicates that not all the features distribution is not of equal interest while modeling acoustic scenes, which is coherent with the typical morphology of acoustic scene which are relatively scarce in terms of events, even if those events can trigger fast perceptual recognition for humans. We thus could consider the acoustic scene as a "skeleton of events on a bed of textures" \cite{nelken_ear_2013}.

If the precise list of events that occur in a given time is unachievable to get even for trained humans, research shows that using only a few events, so called markers \cite{} is enough to reliably predict high level attributes. For example, the presence of a few bird calls in a smooth traffic hubhub is likely to be tagged by humans as a park scene in urban areas \gl{citations ?}.

>>>>

As stated in the introduction, the field of ecoacoustics is relatively young, but significant works are worth mentioning.
One avenue of research, originated in bioacoustics, intends to retrieve the species that produced a given sonic event of relatively short duration, in order to link animal vocalization with behavior\cite{au2008principles, stowell2014large}.
A more recent paradigm processes the audio stream at hand in a holistic way, as it describes the auditory environment over larger temporal scales, without assuming that one single species is present throughout the recording. Automated systems belonging to this paradigm aim at inferring global properties of bioacoustic scenes, including biodiversity indices \vl{ref}, migration patterns \vl{ref}, as well as regions of particular interest before human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.

The same dichotomy applies to the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
In the latter, most state-of-the-art systems roughly follow the bag of frame approach (BOF) initiated in \cite{aucouturier2007bag}, which consists in modeling audio by high-level summary statistics computed from a set of local features.
As it enjoys a high genericity, this approach is found in many audio classification tasks besides ASC.
Yet, the specific implementation with gaussian mixture models (GMM) of Mel-frequency cepstral coefficients (MFCC) it is demonstrated to be perform equivalently compared to a mere averaging of the features  \cite{lagrange:hal-01082501}.
Indeed, the typical morphology of acoustic scenes is of a "skeleton of events on a bed of textures" \cite{nelken_ear_2013}, \ie few impulsive sounds superimposed upon a stationary background.
Therefore, it is arguably more beneficial to focus on the temporal evolution of auditory scenes rather on the joint probability distribution of short-term features.
Interestingly, this statement is validated by auditory psychology as well as sound synthesis based  on summary statistics \cite{mcdermott2013summary}.

Although the precise set of events occuring within a given auditory stream may not be discernable, even for trained humans, research shows that the focus on a few events, so called markers,  sufficed to reliably predict many high-level attributes \cite{} \vl{ref}.
For example, the presence of a few bird calls in a smooth traffic hub is likely to be tagged by humans as a park scene in urban areas \gl{citations ?}.
\vl{Missing transition}
